Dynamical Properties of Molecular Cloud Complexes in Galaxies at the Epoch of Reionization

### 2019-03-12 WRITEUP/ms.tex

@@

The simulation used in this work is described by \citealt{Pallottini17a, Pallottini17b} and is briefly summarized here.
%
\ncode{Serra} is a suite of cosmological zoom-in simulations performed using Eulerian hydrodynamics and adaptive mesh refinement (AMR) technique to achieve high spatial resolution in the region of interest (i.e., regions of high density).
%
In particular, it uses a modified version of \ncode{ramses} \citep{Teyssier2002a} as the AMR backend. Our simulation covers a co-moving box of 20\,Mpc $h$\pmOne in size, resolving down to a physical scale of $l\approx$\,30\,pc (at \z$\sim$\,6) and a (baryonic) mass resolution of $m_b\simeq$\,10$^4$\,\Msun at the finest level. Such a physical scale is close to the size scale of molecular cloud complexes and giant molecular clouds (GMCs) seen in nearby galaxies \citep[e.g.,][]{Sanders85a, Federrath13a, Goodman14a}.
%
We include chemical network in the simulation to trace $\rm{H}$, $\rm{H}^{+}$, $\rm{H}^{-}$, $\rm{He}$, $\rm{He}^{+}$, $\rm{He}^{++}$, $\rm{H}_2$, $\rm{H}_2^{+}$ \citep{Grassi14a,Bovino16a}. Of particular importance to our study here is that our simulation includes non-equilibrium formation of molecular hydrogen (done on-the-fly) to determine the H$_2$ abundance (see \citealt{Pallottini17b} for effects of chemistry affected by non-equilibrium versus equilibrium H$_2$ formation).

@@

Details on the properties of \flower\ --- the main galaxy in our simulation --- are discussed in \citet{Pallottini17b}. Briefly, by \z$\sim$6, \flower is a Lyman-break galaxy (LBG), hosted in a dark matter halo of mass $M_{\rm DM}\simeq$\,10$^{10}$\,\Msun at the center of a cosmic web knot, and accretes mass from the IGM mainly via three filaments of length $\simeq$\,100\,kpc. At \z$\sim$6, \flower has a stellar mass of $M_*\simeq$\,3\E{10}\,\Msun, a metallicity of $Z\simeq$\,0.5\,$Z_{\odot}$, a molecular gas mass of $M_{\rm H2}\simeq$\,5\E{7}\,\Msun, and a globally-integrated SFR of $\simeq$\,100\,\Msun\,yr\pmOne. It is therefore a prototypical galaxy at \z$\sim$\,6.

@@

\begin{figure*}[!htbp]
\centering
\includegraphics[trim=10 0 0 0, clip, width=0.65\textwidth]{\figpath/sfh.pdf}
\caption{
    Star formation history of \flower (top right) and projected stellar mass distribution of \flower during {\it (a)} one of its accretion phases at its early stage of evolution; {\it (b)} one of its major starburst phases after a merger event; and {\it (c)} a relatively quiescent phase post-starburst.\AP{please rearrange the maps such that either i) they have an L shape ii) they are all bewlo the SFR; numbers on the axis are too small, and phase (a) is missing the colorbar; a single colorbar for the star maps might substitute the current 2 ones; please use magma colorbar for the maps (or in any case the colorbar that has been select for for $\Sigma$ trhought the paper)}
\label{fig:SFH}}
\end{figure*}

@@

Given the stochasticity in the \SF history of \flower (see \Fig{SFH}), in \Sec{singless} \AP{but we both give the analysis for 2 stages for maps and all the stages in the scaling relation, is it correct? if so, this point should be made clearer here (or in the next section)} our work is focused on the analysis of two of its most extreme evolutionary stages, to illustrate the salient points of the discussion presented in this paper. The two phases correspond to i) when \flower is accreting materials from its surrounding  and ii) when \flower is undergoing a major starburst phase; such pahses are expected to bracket the most extreme variations in the cloud dynamics.

@@

To identify the molecular complexes, we use a customized version of the clump-finding algorithm available in the \ncode{python} package \ncode{yt} \citep{Turk2011a}, which was initially described in \citet{Smith09a}, but this function has been modified since then.
%
The latest version of the default \ncode{yt} clump finder decomposes the zones in the simulation into non-overlapping tiles, which are stored in a k-dimensional tree (k-d tree). It then identifies the contours of a variable field (here, the density field) within a tile and connects them across the tiles. In the customized version used for this study, we modify the function to enhance the stability of the code.
% (which essentially means we fixed the bugs in order for it to actually work).

@@

\begin{figure*}[htbp]
 \centering
  \includegraphics[scale=0.6]{\figpath/{dual_16_ncut_0.53}.pdf}
  \\ [-2.9em]
  \includegraphics[scale=0.6]{\figpath/{dual_16_ncut_6.81}.pdf}
  \\ [-2.9em]
  \includegraphics[scale=0.6]{\figpath/{dual_16_ncut_18.96}.pdf}
\caption{
Examples showing the MCs identified in our simulation by applying volumetric H$_2$ density cuts of $n_{\rm cut}$\eq[0.53, 6.81,19.00]\,cm$^{-3}$, which is a subset of all the $n_{\rm cut}$ adopted (see text). Color shows the H$_2$ surface density, weighted by the column density. \AP{I would use the label $n_{\rm H2}$ instead of $n({\rm H2})$; i would add the corresponding $n_{cut}= ...$ in withe the lower right corner of each right panel; in the caption I would add which stage is the figure extracted from; optionally, the 3 row might be substituted by a single row with cuts of different colors (if yt allows ...)}
\label{fig:MC}}
% \addtocounter{figure}{-1}
\end{figure*}

In \Fig{h2density}, we show an example of the volumetric H$_2$ density ($n_{\rm H2}$) distribution of \flower~for a given evolutionary stage which includes contributions within $R\sim$\,3.5\,kpc from the galaxy center\footnote{\AP{i would move this note to the (main text of the) section introducing althaea}For reference, the half mass radius of \flower is $\sim$0.5\,kpc and the dark matter virial radius at which the mean enclosed density is 200 times the critical density of the Universe is $r_{\rm 200}$\ssim15\,kpc.}.
%
We note that the distribution is almost flat for $n_{\rm H2}\gtrsim1$\,\cc and it samples the range of density where ``clumps/structures'' are found based on the Euler characteristic, i.e., the fourth Minkowsky functional (see \citealt{Pallottini17b}). We identify MCs by applying 10 equally-spaced volumetric H$_2$ density cuts of $\log{(n_{\rm cut}/{\rm cm^{-3})}}\in[-0.5, 1.5]$\eq[0.32, 0.53, 0.88, 1.45, 2.45, 4.08, 6.81, 11.36, 19.00, 31.62]\footnote{We also vary the range of $n_{\rm cut}$ adopted and find no qualitative differences affecting the results and conclusions of this work except in the slope of the CMF (see \Sec{ncut}).} to the same stage used to plot \Fig{h2density}.

@@

% Molecular clouds are the natal place for \SF, their structure and dynamics hold important clues to understanding
% the mechanisms and physics of formation and evolution of molecular structures and \SF.
Upon identifying the molecular structures, we extract properties such as mass (\AP{we should uniform the notation} $M_{\rm cl}$), effective size ($R$), \AP{introduced here but not used except for comparison with vallini (in the text); maybe we can remove it} Mach number ($\mathcal{M}$), velocity dispersion ($\sigma$), and gas surface density ($\Sigma_{\rm gas}$) to examine their dynamics.

The mass of an MC is calculated from the uniformly-gridded 3D density field, integrating over the MC volume $V$. The effective size is defined assuming spherical geometry, i.e. $R \equiv (3 V /4 \pi)^{1/3}$.
%
In \obs of MC, the linewidths contribution of dense gas contribution is larger then the one from the diffuse gas. We therefore calculate the non-thermal component of the velocity dispersion (\AP{check the definitions, we are using multiple symbols to indicate the same things} $\sigma_{\rm NT}$) of each MC as a density-weighted quantity:
\begin{equation}
\sigma_{\rm NT}^2 = \frac{1}{{3}}\frac{\sum_{i} \rho_i \left|\mathbf{v}_i - \mathbf{\bar v}\right|^2}{\sum_i \rho_i}\,,
\end{equation}
where the sum is done for the cells composing each MC. \AP{I would first introduce the velocity dispersion and the separate them in thermal and non thermal component; also, even $c_s$ is density weighted average} The total velocity dispersion includes contributions from the thermal sound speed ($c_s$):
\begin{equation}
\sigma^2 = \sigma_{\rm NT}^2 + c_s^2.
\end{equation}
The local sound speed of all identified molecular complexes are much smaller compared to the their turbulent velocities\footnote{We find comparable velocity dispersion between that derived from taking the root mean square versus that derived from thermal and non-thermal pressure terms, indicating that rotation velocity is unlikely to be the dominant source of velocity dispersion reported here. \AP{isn t this definition already given in the main text?} In the subsequent sections, we adopt the root mean square of the velocity field as the velocity dispersion ($\sigma$). \label{ftn:veldisp}}. On average, the Mach number of the MCs corresponds to about $\mathcal{M} = \sigma_{\rm NT}/c_s\approx 50$. This is consistent with the global analysis done on \flower by \citet{Vallini18a}.

We show in \Fig{dist} the MC distributions in terms of their molecular gas masses, radii, and gas mass fractions, which we define as
\begin{equation}
f_{\rm gas} = \frac{M_{\rm H2}} {\left(M_{\rm H2} + M_*\right)},
\end{equation}
where $M_*$ is the stellar mass withing the MC volume.
%
We note that the distributions vary for different evolutionary stage of \flower. The highest density threshold of $n_{\rm cut}$\eq31.62\,\cc yields a ``minimum'' MC mass of the order of 10$^{6.5}$\,\Msun for the densest MC.
%
We find $\sim$10$-$13 MCs with masses exceeding 10$^8$\,\Msun across all the considered evolutionary stages for each of the given $n_{\rm cut}$ (see \Sec{method}). The mass of the MCs identified ranges between $M_{\rm cl}\approx$10$^{6.5-9}$\,\Msun, consistent with those observed in \z$\sim$2 galaxies in rest-frame {\it UV and optical light} \citep{Elmegreen07a, Elmegreen09a}.

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.7\textwidth]{\figpath/minmaxNcut_basicDistributions.png}
\caption{Distributions of mass, size, and gas mass fraction of MCs identified using the lowest $n_{\rm cut}$ (left panels) and $n_{\rm ncut}$\eq18.96\,\cc (right panels).
%
Note that the scale shown on the y-axes are different between the left and right panels, as less MCs are identified at higher $n_{\rm cut}$.
\AP{it is a bit difficult to read the xaxis label; an option (but i'm not sure if it will work) would be to have a 3x2 alignment, and keeping the same axis range for both cuts (for easier visual comparison)}
\label{fig:dist}}
\end{figure*}

@@

% Relating Larson's law to stability and pressure (perhaps move this to other section?).
In general, the virial theorem for a distribution of gas can be written as
\begin{equation}\label{eqn:virial_th_general}
\frac{1}{2}\ddot I = 2(T - T_{\rm ext}) + W,
\end{equation}
where $\ddot I$ is the second time derivative of the Lagrangian moment of inertia, $T$ is the internal energy of the gas, $T_s$ is external pressure support, and $W$ is the gravity energy.
%
Let us specialize to the case of a spherical self-gravitating molecular cloud of mass \AP{check the definitions} $M$, radius $R$, and velocity dispersion $\sigma$, accounting for both thermal and turbulent velocity dispersion. Neglecting magnetic field and calling $P_{\rm ext}$ the external pressure, \Eq{virial_th_general} can be written as
\begin{equation}
\frac{1}{2}\ddot I = 3 M \sigma^2 - 4\pi P_{\rm ext} R - \frac{\Gamma GM^2}{R}\,,
\label{eqn:virial}
\end{equation}
where $\Gamma$ is a geometrical factor that is equal to 3/5 for a uniform sphere; in \Eq{virial} the first term on the right hand side (RHS) is the pressure term from internal velocity dispersion, the second term the external pressure term, and the third term is is the gravity term. For the case of simple virial equilibrium (SVE; i.e., equilibrium state without external pressure), \Eq{virial} becomes:
\begin{equation}
\alpha_{\rm vir} \equiv \frac{3\sigma^2}{\Gamma GM/R} = \frac{5\sigma^2R}{GM}\,,
\label{eqn:alpha}
\end{equation}
where we have defined the virial parameter $\alpha_{\rm vir}$. It is convenient to introduce \AP{i do not fully follow the logic of the following passages}
\begin{equation}
V_0^2\equiv\frac{\sigma^2}{R},\,
\end{equation}
which is related to Larson's linewidth-size relation \citep{Larson81a}, which can be recast into the form of:
\begin{equation}
\sigma^2/R = \pi G \Sigma/5.
\end{equation}
For pressure-bounded virial equilibrium (PVE; i.e. equilibrium state with pressure), % external pressure
Equation~\ref{eqn:virial} becomes:
\begin{equation}
P_{\rm ext} = \frac{3\sigma^2M}{4\pi R^3} - \frac{\Gamma G M^2}{4\pi R^4},
\label{eqn:pext}
\end{equation}
which describes the external pressure needed to confine the gas inside a volume $V$. \AP{please specify which eq.s you are referring to} Rearranging the equation and substituting for the surface density $\Sigma$\eq$M/\pi R^2$, we can express this equation using the following:
\begin{equation}
\frac{\sigma^2}{R} = \frac{1}{3}\left(\frac{4P_{\rm ext}}{\Sigma} + \Gamma G \Sigma \pi \right).
\label{eqn:v0}
\end{equation}
Therefore, for a virialized cloud, one expects a one-to-one mapping between $V_0^2$ and $\Sigma$ since $\sigma^2/R\propto\Sigma$, whereas Equation~\ref{eqn:v0} represents the locus along which external pressures $P_{\rm ext}$ are needed in order for MCs to have linewidths $\sigma$ for a given set of surface densities. % (see\Fig{alpha27}).
In other words, \AP{the following is a bit unclear} a cloud with $\sigma$ and $\Sigma$ offset from $\sigma^2/R\mapsto\Sigma$ is in equilibrium with the external pressure $P_{\rm ext}$ (and therefore $V_0^2$ is not constant with $\Sigma$ but varies depending on $P_{\rm ext}$; cf. expectation for SVE, where $\sigma\propto R^{0.5}$; see e.g., \citealt{Heyer09a, Hughes10a, Hughes13b, Meidt13a}).

Summarizing, to quantify the stability of MC we use the virial parameter (\Eq{alpha}), which describes the balance between kinetic and gravitational potential energies. An $\alpha_{\rm vir}\approx$\,2 corresponds to approximately equipartition between the two energy terms and is often used to assess the boundedness of a given structure \citep[see e.g., ][]{Kauffmann17b}\footnote{Note, however, that the true virial state/boundedness of a given structure also depends on the surface terms and the magnetic field (see \Eq{virial}).}.

@@

The onset of gravitational instability is considered to be tightly connected to \SF \citep[e.g.,][]{Kennicutt89a, Wang94a, Li05b, Li06a}. \AP{i think we can partially cut the following} From virial theorem, Jeans instability sets the scales at which gravitational potential overcomes the internal energy. Namely, gravitational instabilities dominates at scales $L > L_J$, where $L_J$ is the Jeans length. However, centrifugal force resulting from differential rotation in disk galaxies can inhibit collapse even on these scales. As a result, a disk is thought to be unstable on scales between $L_J < L < L_{\rm rot}$, where $L_{\rm rot}$ is set by the surface density of the disk and the angular velocity of the rotation.

In theoretical and observational works, gravitational instability has been widely discussed in the context of the Toomre stability criterion \citep{Toomre64a, Goldreich65b}, or the Toomre $Q$ parameter (\AP{i would put this parenthesis as a note later on, i.e. close to \Eq{q_eff}} or the proxy, circular velocity to dispersion ratio; $v_{\rm circ}/\sigma$; e.g., \citealt{GarciaBurillo03a, Genzel11a, Kassin12a, Leung19a}).
% https://ned.ipac.caltech.edu/level5/March15/Glazebrook/Glazebrook5.html
%
% from linear analysis
For {\it axisymmetric} mode, the dispersion relation for the growth of density perturbation in a rotating turbulent disk of \AP{does this hold for a thin disk?}finite thickness $h$ is described by \AP{do we have a classical reference to add here?}:
\begin{equation}
\omega^2 = \kappa^2 - \frac{2\pi G \Sigma |k|}{1 + |k| h} + \sigma^2 k^2\,,
\label{eqn:3Ddisp}
\end{equation}
where $k$ is the wavenumber and $\kappa$ is the epicyclic frequency, defined as:
\begin{equation}
\kappa^2\equiv\frac{2\Omega}{R}\frac{d}{dR}\left(R^2\Omega\right).
\label{eqn:kappa}
\end{equation}
The first term on the RHS of Equation~\ref{eqn:3Ddisp} describes rotation support, whereas the second term describes self-gravity, and the third term describes internal pressure support. Then the Toomre-Q parameter can be defined as \citep{Toomre64a}:
\begin{equation}
Q_{\rm gas}\equiv\frac{\sigma\kappa}{\pi G \Sigma}\,.
\label{eqn:Q}
\end{equation}
In the thin disk approximation ($kh\ll1$), the solution of \Eq{3Ddisp} is unstable for scales $k$ such that $Q < 1$ (or equivalently $\omega^2 < 0$). Physically, this situation happens when local gravitational instability 
overcomes support from pressure and rotation, allowing fragmentation and collapse to happen.
% but further evolution depends on their EOS. (e.g., instability impose by angular momentum from gas accretion from the cosmic web and satellite galaxies and stellar feedback).
% Note that fragmentation is expected to happen at critical scale length $\lambda_{\rm crit} < 2 \pi^2 G \Sigma / \kappa^2$, which is greater than the typical size of  GMCs. It should be clear that the instability sets the scales for fragmentation, but star-forming GMCs are the collapsing, denser, and cooler molecular structures on even smaller scales. The fragmented structures thus correspond to regions where $Q\lesssim1.
Similarly, for a collisionless fluid -- as an ensamble of stars -- the Toomre $Q$ parameter is defined by \citep{Toomre64a}:
\begin{equation}
Q_{\rm star} \equiv\frac{\sigma\kappa}{3.36 G \Sigma}\,.
\end{equation}

>>>>

\DL{Maybe we will have to do it that way, and I will manually maintain my copy on the repo and on my macbook?}

@@

The simulation used in this work is described by \citealt{Pallottini17a, Pallottini17b} and is briefly summarized here.
%
\ncode{Serra} is a suite of cosmological zoom-in simulations performed using Eulerian hydrodynamics and adaptive mesh refinement (AMR) technique to achieve high spatial resolution in the region of interest (i.e., regions of high density).
%
In particular, it uses a modified version of \ncode{ramses} \citep{Teyssier02a} as the AMR backend. Our simulation covers a co-moving box of 20\,Mpc $h$\pmOne in size, resolving down to a physical scale of $l\approx$\,30\,pc (at \z$\sim$\,6) and a (baryonic) mass resolution of $m_b\simeq$\,10$^4$\,\Msun at the finest level. Such a physical scale is close to the size scale of molecular cloud complexes and giant molecular clouds (GMCs) seen in nearby galaxies \citep[e.g.,][]{Sanders85a, Federrath13a, Goodman14a}.
%
We include chemical network in the simulation to trace $\rm{H}$, $\rm{H}^{+}$, $\rm{H}^{-}$, $\rm{He}$, $\rm{He}^{+}$, $\rm{He}^{++}$, $\rm{H}_2$, $\rm{H}_2^{+}$ \citep{Grassi14a,Bovino16a}. Of particular importance to our study here is that our simulation includes non-equilibrium formation of molecular hydrogen (done on-the-fly) to determine the H$_2$ abundance (see \citealt{Pallottini17b} for effects of chemistry affected by non-equilibrium versus equilibrium H$_2$ formation).

@@

Details on the properties of \flower\ --- the main galaxy in our simulation --- are discussed in \citet{Pallottini17b}. Briefly, by \z$\sim$6, \flower is a Lyman-break galaxy (LBG), hosted in a dark matter halo of mass $M_{\rm DM}\simeq$\,10$^{10}$\,\Msun at the center of a cosmic web knot, and accretes mass from the IGM mainly via three filaments of length $\simeq$\,100\,kpc. At \z$\sim$6, \flower has a stellar mass of $M_*\simeq$\,3\E{10}\,\Msun, a metallicity of $Z\simeq$\,0.5\,$Z_{\odot}$, a molecular gas mass of $M_{\rm H2}\simeq$\,5\E{7}\,\Msun, and a globally-integrated SFR of $\simeq$\,100\,\Msun\,yr\pmOne. It is therefore a prototypical galaxy at \z$\sim$\,6.
For reference, the half mass radius of \flower is $\sim$0.5\,kpc and the dark matter virial radius at which the mean enclosed density is 200 times the critical density of the Universe is $r_{\rm 200}\simeq$\,15\,kpc.

@@

\begin{figure*}[!htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.65\textwidth]{\figpath/sfh.pdf}
\caption{
    Star formation history of \flower (top right) and projected stellar mass distribution of \flower during {\it (a)} one of its accretion phases at its early stage of evolution; {\it (b)} one of its major starburst phases after a merger event; and {\it (c)} a relatively quiescent phase post-starburst.
\label{fig:SFH}}
\end{figure*}

@@

Given the stochasticity in the \SF history of \flower (see \Fig{SFH}), we focus this work on the analysis of two of its most extreme evolutionary 
stages (see \Sec{singless}), to illustrate the salient points of discussion presented in this paper.
The two phases correspond to i) when \flower 
is accreting materials from its surrounding  and ii) when \flower is undergoing a major starburst phase; such phases are expected to bracket the most extreme variations in the cloud dynamics. 
For completeness, we also show the results (in terms of the scaling relations presented) for 
the other evolutionary stages traced in the simulation.

Throughout this paper, we call ``satellite galaxies'' as dense gas regions outside the main disk of \flower,
which is $\sim$\,1\,kpc in radius.

@@

To identify the molecular complexes, we use a customized version of the clump-finding algorithm available in the \ncode{python} package \ncode{yt} \citep{Turk11a}, which was initially described in \citet{Smith09a}, but this function has been modified since then.
%
The latest version of the default \ncode{yt} clump finder decomposes the zones in the simulation into non-overlapping tiles, which are stored in a k-dimensional tree (k-d tree). It then identifies the contours of a variable field (here, the density field) within a tile and connects them across the tiles. In the customized version used for this study, we modify the function to enhance the stability of the code.
% (which essentially means we fixed the bugs in order for it to actually work).

@@

\begin{figure*}[htbp]
 \centering
  \includegraphics[scale=0.6]{\figpath/{dual_16_ncut_0.53}.pdf}
  \\ [-2.9em]
  \includegraphics[scale=0.6]{\figpath/{dual_16_ncut_6.81}.pdf}
  \\ [-2.9em]
  \includegraphics[scale=0.6]{\figpath/{dual_16_ncut_18.96}.pdf}
\caption{
Examples showing the MCs identified in the accreting phase of \flower by applying volumetric H$_2$ density cuts of $n_{\rm cut}$\eq[0.53, 6.81,19.00]\,cm$^{-3}$, which is a subset of all the $n_{\rm cut}$ adopted (see text). Color shows the H$_2$ surface density, weighted by the column density. 
\label{fig:MC}}
% \addtocounter{figure}{-1}
\end{figure*}

In \Fig{h2density}, we show an example of the volumetric H$_2$ density ($n_{\rm H2}$) distribution of \flower~for a given evolutionary stage which includes contributions within $R\sim$\,3.5\,kpc from the galaxy center.
%
We note that the distribution is almost flat for $n_{\rm H2}\gtrsim1$\,\cc and it samples the range of density where ``clumps/structures'' are found based on the Euler characteristic, i.e., the fourth Minkowsky functional (see \citealt{Pallottini17b}). We identify MCs by applying 10 equally-spaced volumetric H$_2$ density cuts of $\log{(n_{\rm cut}/{\rm cm^{-3})}}\in[-0.5, 1.5]$\eq[0.32, 0.53, 0.88, 1.45, 2.45, 4.08, 6.81, 11.36, 19.00, 31.62]\footnote{We also vary the range of $n_{\rm cut}$ adopted and find no qualitative differences affecting the results and conclusions of this work except in the slope of the CMF (see \Sec{ncut}).} to the same stage used to plot \Fig{h2density}.

@@

% Molecular clouds are the natal place for \SF, their structure and dynamics hold important clues to understanding
% the mechanisms and physics of formation and evolution of molecular structures and \SF.
Upon identifying the molecular structures, we extract properties such as the H$_2$ gas mass ($M_{\rm cl}$), effective size ($R$), Mach number ($\mathcal{M}$), velocity dispersion ($\sigma$), and gas surface density ($\Sigma_{\rm gas}$) to examine their dynamics.

The mass of an MC is calculated from the uniformly-gridded 3D density field, integrating over the MC volume $V$. The effective size is defined assuming spherical geometry, i.e. $R \equiv (3 V /4 \pi)^{1/3}$.
%
The velocity dispersion of MCs is calculated from non-thermal velocity dispersion ($\sigma_{\rm NT}$) and thermal sound speed ($c_s$):
\begin{equation}
\sigma^2 = \sigma_{\rm NT}^2 + c_s^2.
\label{eqn:veldisp}
\end{equation}
% 
In \obs of MC, the linewidths contribution of dense gas contribution is larger then the one from the diffuse gas. We therefore calculate 
each term on the RHS of Equation~\ref{eqn:veldisp} as a density-weighted quantity. For instance, the non-thermal velocity dispersion is 
calculated as follows:
\begin{equation}
\sigma_{\rm NT}^2 = \frac{1}{{3}}\frac{\sum_{i} \rho_i \left|\mathbf{v}_i - \mathbf{\bar v}\right|^2}{\sum_i \rho_i}\,,
\end{equation}
where the sum is done for the cells composing each MC.
The local sound speed of all identified molecular complexes are much smaller compared to the their turbulent velocities\footnote{We find comparable velocity dispersion between that derived from taking the root mean square versus that derived from thermal and non-thermal pressure terms, indicating that rotation velocity is unlikely to be the dominant source of velocity dispersion reported here.}. On average, the Mach number of the MCs corresponds to about $\mathcal{M} = \sigma_{\rm NT}/c_s\approx 50$. This is consistent with the global analysis done on \flower by \citet{Vallini18a}.

We show in \Fig{dist} the MC distributions in terms of their molecular gas masses, radii, and gas mass fractions, which we define as
\begin{equation}
f_{\rm gas} = \frac{M_{\rm cl}} {\left(M_{\rm cl} + M_*\right)},
\end{equation}
where $M_*$ is the stellar mass within the MC volume.
%
We note that the distributions vary for different evolutionary stage of \flower. The highest density threshold of $n_{\rm cut}$\eq31.62\,\cc yields a ``minimum'' MC mass of the order of 10$^{6.5}$\,\Msun for the densest MC.
%
We find $\sim$10$-$13 MCs with masses exceeding 10$^8$\,\Msun across all the considered evolutionary stages for each of the given $n_{\rm cut}$ (see \Sec{method}). The mass of the MCs identified ranges between $M_{\rm cl}\approx$10$^{6.5-9}$\,\Msun, consistent with those observed in \z$\sim$2 galaxies in rest-frame {\it UV and optical light} \citep{Elmegreen07a, Elmegreen09a}.

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=\textwidth]{\figpath/minmaxNcut_basicDistributions.pdf}
\caption{Distributions of mass (left), size (middle), and gas mass fraction (right) of MCs identified using the lowest $n_{\rm cut}$ (top panels) and $n_{\rm ncut}$\eq18.96\,\cc (bottom panels).
Note that the scale shown on the y-axes are different between the top and bottom panels, as less MCs are identified at higher $n_{\rm cut}$.
\label{fig:dist}}
\end{figure*}

@@

% Relating Larson's law to stability and pressure (perhaps move this to other section?).
In general, the virial theorem for a distribution of gas can be written as
\begin{equation}\label{eqn:virial_th_general}
\frac{1}{2}\ddot I = 2(T - T_{\rm ext}) + W,
\end{equation}
where $\ddot I$ is the second time derivative of the Lagrangian moment of inertia, $T$ is the internal energy of the gas, $T_s$ is external pressure support, and $W$ is the gravity energy.
%
Let us specialize to the case of a spherical self-gravitating molecular cloud of mass $M_{\rm cl}$, radius $R$, and velocity dispersion $\sigma$, accounting for both thermal and turbulent velocity dispersion. Neglecting magnetic field and calling $P_{\rm ext}$ the external pressure, \Eq{virial_th_general} can be written as
\begin{equation}
\frac{1}{2}\ddot I = 3 M_{\rm cl} \sigma^2 - 4\pi P_{\rm ext} R - \frac{\Gamma GM_{\rm cl}^2}{R}\,,
\label{eqn:virial}
\end{equation}
where $\Gamma$ is a geometrical factor that is equal to 3/5 for a uniform sphere; in \Eq{virial} the first term on the right hand side (RHS) is the pressure term from internal velocity dispersion, the second term the external pressure term, and the third term is is the gravity term. For the case of simple virial equilibrium (SVE; i.e., equilibrium state without external pressure), \Eq{virial} becomes:
\begin{equation}
\alpha_{\rm vir} \equiv \frac{3\sigma^2}{\Gamma GM_{\rm cl}/R} = \frac{5\sigma^2R}{GM_{\rm cl}}\,,
\label{eqn:alpha}
\end{equation}
where we have defined the virial parameter $\alpha_{\rm vir}$.

\AP{i do not fully follow the logic of the following passages}
\DL{need some work to clarify this para}
Motivated by the Larson's relations, we express the observable quantities in the following forms:
\begin{equation}
V_0^2\equiv\frac{\sigma^2}{R},\,
\end{equation}
which is related to Larson's linewidth-size relation \citep{Larson81a}, which can be recast into the form of:
\begin{equation}
\sigma^2/R = \pi G \Sigma/5.
\end{equation}
For pressure-bounded virial equilibrium (PVE; i.e. equilibrium state with pressure), % external pressure
Equation~\ref{eqn:virial} becomes:
\begin{equation}
P_{\rm ext} = \frac{3\sigma^2M_{\rm cl}}{4\pi R^3} - \frac{\Gamma G M_{\rm cl}^2}{4\pi R^4},
\label{eqn:pext}
\end{equation}
which describes the external pressure needed to confine the gas inside a volume $V$. \AP{please specify which eq.s you are referring to} Rearranging the equation and substituting for the surface density $\Sigma$\eq$M/\pi R^2$, we can express this equation using the following:
\begin{equation}
\frac{\sigma^2}{R} = \frac{1}{3}\left(\frac{4P_{\rm ext}}{\Sigma} + \Gamma G \Sigma \pi \right).
\label{eqn:v0}
\end{equation}
Therefore, for a virialized cloud, one expects a one-to-one mapping between $V_0^2$ and $\Sigma$ since $\sigma^2/R\propto\Sigma$, whereas Equation~\ref{eqn:v0} represents the locus along which external pressures $P_{\rm ext}$ are needed in order for MCs to have linewidths $\sigma$ for a given set of surface densities. % (see\Fig{alpha27}).
In other words, \AP{the following is a bit unclear} a cloud with $\sigma$ and $\Sigma$ offset from $\sigma^2/R\mapsto\Sigma$ is in equilibrium with the external pressure $P_{\rm ext}$ (and therefore $V_0^2$ is not constant with $\Sigma$ but varies depending on $P_{\rm ext}$; cf. expectation for SVE, where $\sigma\propto R^{0.5}$; see e.g., \citealt{Heyer09a, Hughes10a, Hughes13b, Meidt13a}).

Summarizing, to quantify the stability of MC we use the virial parameter (\Eq{alpha}), which describes the balance between kinetic and gravitational potential energies. An $\alpha_{\rm vir}\approx$\,2 corresponds to approximately equipartition between the two energy terms and is often used to assess the boundedness of a given structure in \obs \citep[see e.g., ][]{Kauffmann17b}\footnote{Note, however, that the true virial state/boundedness of a given structure also depends on the surface terms and the magnetic field (see \Eq{virial}).}.
To facilitate comparison with \obs, we derive $\alpha_{\rm vir}$ using the gas component only and ignore contributions due to 
the stellar component.

@@

The onset of gravitational instability is considered to be tightly connected to \SF \citep[e.g.,][]{Kennicutt89a, Wang94a, Li05b, Li06a}. \AP{i think we can partially cut the following} \DL{probably, but I am just being explicit here to help remind myself what am I trying to say.}
From virial theorem, Jeans instability sets the scales at which gravitational potential overcomes the internal energy. Namely, gravitational instabilities dominates at scales $L > L_J$, where $L_J$ is the Jeans length. However, centrifugal force resulting from differential rotation in disk galaxies can inhibit collapse even on these scales. As a result, a disk is thought to be unstable on scales between $L_J < L < L_{\rm rot}$, where $L_{\rm rot}$ is set by the surface density of the disk and the angular velocity of the rotation.

In theoretical and observational works, gravitational instability has been widely discussed in the context of the Toomre stability criterion \citep{Toomre64a, Goldreich65b}, or the Toomre $Q$ parameter (\AP{i would put this parenthesis as a note later on, i.e. close to \Eq{q_eff}} or the proxy, circular velocity to dispersion ratio; $v_{\rm circ}/\sigma$; e.g., \citealt{GarciaBurillo03a, Genzel11a, Kassin12a, Leung19a}).
% https://ned.ipac.caltech.edu/level5/March15/Glazebrook/Glazebrook5.html
%
% from linear analysis
For {\it axisymmetric} mode, the dispersion relation for the growth of density perturbation in a rotating turbulent disk of 
finite thickness $h$ is described by 
\begin{equation}
\omega^2 = \kappa^2 - \frac{2\pi G \Sigma |k|}{1 + |k| h} + \sigma^2 k^2\,,
\label{eqn:3Ddisp}
\end{equation}
where $k$ is the wavenumber and $\kappa$ is the epicyclic frequency, defined as:
\begin{equation}
\kappa^2\equiv\frac{2\Omega}{R}\frac{d}{dR}\left(R^2\Omega\right)\,,
\label{eqn:kappa}
\end{equation}
\citep{Romeo92a}.
The first term on the RHS of Equation~\ref{eqn:3Ddisp} describes rotation support, whereas the second term describes self-gravity, and the third term describes internal pressure support. Then the Toomre-Q parameter can be defined as \citep{Toomre64a}:
\begin{equation}
Q_{\rm gas}\equiv\frac{\sigma\kappa}{\pi G \Sigma}\,.
\label{eqn:Q}
\end{equation}
In the thin disk approximation ($kh\ll1$), the solution of \Eq{3Ddisp} is unstable for scales $k$ such that $Q < 1$ (or equivalently $\omega^2 < 0$). Physically, this situation happens when local gravitational instability 
overcomes support from pressure and rotation, allowing fragmentation and collapse to happen.
% but further evolution depends on their EOS. (e.g., instability impose by angular momentum from gas accretion from the cosmic web and satellite galaxies and stellar feedback).
% Note that fragmentation is expected to happen at critical scale length $\lambda_{\rm crit} < 2 \pi^2 G \Sigma / \kappa^2$, which is greater than the typical size of  GMCs. It should be clear that the instability sets the scales for fragmentation, but star-forming GMCs are the collapsing, denser, and cooler molecular structures on even smaller scales. The fragmented structures thus correspond to regions where $Q\lesssim1.
Similarly, for a collisionless fluid -- as an ensamble of stars -- the Toomre $Q$ parameter is defined by \citep{Toomre64a}:
\begin{equation}
Q_{\rm star} \equiv\frac{\sigma\kappa}{3.36 G \Sigma}\,.
\end{equation}
